---
title: "utilscognigen options"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{utilscognigen options}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(utilscognigen)
```

# Configuration options

These are settings that can be controlled with `options()`. Set the desired options in your .Rprofile. Do not set these options in production code; none of these options control behavior in non-interactive R sessions.

## `cli.num_colors`

This is a `cli` option that controls the number of ANSI colors. Set `options(cli.num_colors = 0)` to turn off ANSI colors. In CPP's production environments, ANSI colors are disabled by default. See `cli::num_ansi_colors()`. See also the `cli.default_num_colors` option.

## `utilscognigen.cd_focus`

This option controls whether `cd()` shows the working directory in the RStudio Files pane.

## `utilscognigen.rcb_as_job`

This option controls whether `rcb()` tries to execute the programs as an RStudio Job.

## `utilscognigen.path_shared_code`

This should be the file path to a directory with some form of shared R code that is expected to be copied.

## `utilscognigen.gitlab_host_url`

This should be the URL that GitLab projects are hosted under.

## `utilscognigen.outlook_groups_url`

This should be the URL that Outlook group emails are under.

## `utilscognigen.sharepoint_sites_url`

This should be the URL that SharePoint sites are under.
